Constant Error Tolerance Computational Fuzzy Extractors

### 2014-02-07 trunk/constantRate/ConstCompFuzzExt.tex
finished intro draft

\section{Introduction}\label{sec:introduction}
\lnote{What I want to do with this: make it clear that we are not the crazy obfuscation types, but are using something practically achievable; perhaps mention RO; perhaps compare with Dodis' RO analysis (was that for robustness only?); explain that we have two points on an entropy/error tolerance tradeoff; explain how switching to computational makes our construction possible and, in general, why our construction is cool. Section titles for 4 and 5!}

\paragraph{Fuzzy Extractors}
Cryptography relies on secrets for that are read multiple times for key derivation and authentication. However, many sources with sufficient secrecy  provide similar but not identical values at each reading~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
physically unclonable functions~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical}, 
and quantum information~\cite{bennett1988privacy}). Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
Both of these problems have interactive and noninteractive versions.  In this paper, we are interested the noninteractive case, which can be used, in particular, by  a single user trying to produce the same key from multiple readings of a physical source at different times.  The primitive accomplishing information reconciliation and privacy amplification noninteractively is known as a \emph{fuzzy extractor}; it is defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}

Fuzzy extractors consist of a pair of algorithms: \gen takes a source value $w$, and produces a key $r$ and a public helper value $p$.  The second algorithm \rep takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.  The security guarantee is that $r$ produces by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$, as long as $w$ has sufficient min-entropy $m$. The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on strings over some alphabet $\mathcal{Z}$ of length $\ell$).

@@

More generally, let $B_t$ denote the number of points in a ball of radius $t$. For any $m$ and $t$, one can come up with a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of all points in several nonoverlapping balls of radius $t$ (we need the space to be sufficiently large for the balls to fit). We thus call $m-\log B_t$ the \emph{usable} entropy, denoted by $\Huse$. The previous paragraph shows that  no fuzzy extractor can handle $\Huse\le 0$ as long as we require it work for \emph{all} distributions of a given min-entropy.

@@

\paragraph{Our Contributions}
We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse<0$ over $\mathcal{Z}^\ell$ for a large alphabet $\mathcal{Z}$.  As already explained above, such constructions cannot work without some restrictions on the distribution. The first construction works when every single symbol of $w$ has individual superlogarithmic min-entropy (thus requiring a large alphabet), but allows for arbitrary dependence between symbols (the actual condition is more general and may permit some symbols to have less entropy; see \defref{def:block guessable}).

We improve the entropy requirement in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
However, this improvement comes at a price to error-tolerance: whereas the first construction tolerates a constant fraction of errors, the second construction tolerates $O(\ell/\log\ell)$ errors.\lnote{check}.

\paragraph{Our Approach}
Our constructions are computationally secure. Indeed, known techniques for proving information-theoretically secure fuzzy extractors work for all distributions of a given entropy, and thus cannot be used to prove security for some distributions of with $\Huse\le 0$ (because then they would prove security for all distributions with $\Huse \le 0$, which we know is impossible.)

Most known constructions of fuzzy extractors put sufficient information in $p$ to recover $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
Fuller, Meng, and Reyzin~\cite{fuller2013computational}, in introducing computational fuzzy extractors, show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.  Instead, they suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent high-entropy secret instead of recovering $w$.  We take the second approach.

The procedure that takes a high-entropy input to get a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}. Since in our case, the resulting entropy is computational, we define and show two constructions of \emph{computational fuzzy conductors}. 
These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).

Both constructions are based on the obfuscation of point programs~\cite{canetti1997towards}.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$. 
We need a strong version of point obfuscation, which is secure under composition.  
However, we note that for even this strong version, obfuscation of point programs is much simpler and more efficient than general obfuscation. In particular, it is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}; it is may also be reasonable to assume that a cryptographic hash function, such as SHA-2, is a good point obfuscator. \lnote{cite anything?} \lnote{where should this fit in:
it can be achieved under generic cryptographic hardness assumptions~\cite{wee2005obfuscating} -- can the strong variant be achieved by Wee?}

Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.

\lnote{stopped here}

\textbf{\consref{cons:first construction}: }
Consider a source $W = W_1,..., W_\ell$ that is split into blocks~(over a large alphabet).  We would like to tolerate errors in $t$ individual blocks.  For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$.  This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.  With a close value $w'$, $\rec$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.  For most locations $i$, \rep can determine whether $w_i$ or a random value was obfuscated.  Thus, most bits of $c_i$ are recoverable. To tolerate errors we sample the coins $c$ from the codewords of an error-correcting code.  The set of possible codewords forms a high entropy distribution.  This construction conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.

In \consref{cons:first construction}, each block of $W$ is individually obfuscated.  This has two drawbacks, first an adversary may learn the value of some blocks which may be sensitive information.  Second, security only holds for sources where a large number of blocks have super-logarithmic entropy~(\defref{def:block guessable}).  Our second construction addresses these problems.

\textbf{\consref{cons:sampling}: }
As before we consider a source $W=W_1,...,W_\ell$ that is split into blocks.  However, instead of obfuscating individually
blocks individually, for each bit $c_i$ we randomly select a subset of blocks.  These blocks are concatenated and obfuscated together.  By sampling, we can significantly decrease the entropy requirement on individual blocks.  This paradigm is similar to the \emph{sample-then-extract} paradigm in the locally-computable extractor literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason, we call \consref{cons:sampling} \emph{sample-then-obfuscate}.

%Our construction provides several advantages over previous constructions of computational fuzzy extractors:
%\begin{itemize}
%\item The first computational fuzzy extractor where $\Huse$ may be negative for a large class of distributions.\item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
%\item The first computational fuzzy extractor where blocks are not required to be uniformly distributed.  Our construction simply requires a large number of blocks that are unguessable given equality queries.  This subsumes the distributions supported by~\cite[Construction 4.1]{fuller2013computational}.
%\end{itemize}

\textbf{Limitations: } In order to achieve security with $\Huse<0$, our alphabet~(for Hamming distance) must be super-polynomial in the security parameter.  Our constructions are applicable for sources where many bits are expected to err consecutively, followed by many consecutive correct bits~(known as burst errors~\cite{gilbert1960capacity}).  Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.  Furthermore, we may leak sensitive information about the underlying source $W$.  In \consref{cons:first construction} it is possible to learn the value of individual blocks $W_i$.  Our two constructions are not noisy point obfuscation for any reasonable definition of obfuscation.  Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} achieve a notion of noisy point obfuscation when $\Huse>>0$ using a information-reconciliation component that hides all partial information.  Constructing noisy point obfuscation for all sources remains an open problem.

The second construction does not require a large alphabet.  However, because of its lower error tolerance, $\Huse<0$ only for large alphabets (and if $\Huse>0$, then there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}).
It would be nice to get information-theoretic security, but current techniques seem to work for all distributions, which we know is impossible.

\lnote{old stuff below}

Fuzzy extractors have not yielded key derivation for all noisy sources.
There is tension between security and error-tolerance.  The key should be uniform to an observer but nearby $w'$ should map to the same key.  By nearby, we mean that $\dis(w, w')\leq t$ for some metric $\dis$.  In the information-theoretic realm, increasing $t$ means a decrease in the strength of the key $r$.  This is because a fuzzy extractor can be converted into an error correcting code~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  The length of the key $r$ is dictated by size of the best code that corrects $t$ errors.  Error-correcting codes are well studied and we have tight bounds on this quantity. % how many codewords may be in a code that corrects $t$ errors.

We consider the Hamming metric.  For the Hamming metric, there exists a distribution $W$ where the key derived from $W$ may be no longer than the difference between the starting entropy of the source and logarithm of the number of error patterns to be corrected~(and we have constructions of fuzzy extractors that nearly meet this bound). For the remainder of this paper we call this difference the minimum usable entropy, denoted $\Huse$.  This represents a practical problem as important biometrics have $\Huse<0$~(see \apref{sec:iris no key}).

 %let $|B_t|$ be the number of points within distance $t$.  The length of the key $|r| < \Hoo(W) - \log |B_t|$~(see~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} for the precise conditions).  For the remainder of this paper, we denote this quantity by $\Huse = \Hoo(W) - \log |B_t|$.

To achieve security when $\Huse<0$, some restriction on the source distribution $W$ is necessary~(minimal conditions are discussed in~\apref{sec:minimal conditions}).  However, the tools for constructing information-theoretic fuzzy extractors have not yielded natural restrictions.  Fuller, Meng, and Reyzin define a computationally-secure version of fuzzy extractors~\cite{fuller2013computational}.  Computational fuzzy extractors produce pseudorandom instead of truly random keys.  A computational fuzzy extractor may exist for a larger class of distributions with $\Huse<0$ than is possible information-theoretically.

In this work, we construct computational fuzzy extractors when $\Huse<0$ for large classes of distributions.
In the computational setting, a key may be expanded once it is long enough to serve as input to a computational extractor.  We focus on providing a reasonable length key when $\Huse<0$.

The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.

@@

\begin{definition}
\label{def:fuzzy min-ent}
A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
\[
\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
\]
\end{definition}
For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item On input $r, p$.
\item If $\rep(m, p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
\end{proof}
\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.  This means that fuzzy min-entropy is also a necessary condition for interactive solution.  %The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.  
If we wish to support parameter regimes where $\Huse<0$ there is some distribution with $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution over points within distance $t$).  Thus, if the analysis of a fuzzy extractor is for all input distributions with a particular $\Huse$, no key can be output when $\Huse<0$.   This motivates our restriction to meaningful classes of source distributions with $\Huse<0$.
%This means we inherently must talk about the security and errors together.

>>>>

\section{Introduction}\label{sec:introduction}

\paragraph{Fuzzy Extractors}
Cryptography relies on secrets for that are read multiple times for key derivation and authentication. However, many sources with sufficient randomness  provide similar but not identical values at each reading~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
physically unclonable functions~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical}, 
and quantum information~\cite{bennett1988privacy}). Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
Both of these problems have interactive and noninteractive versions.  In this paper, we are interested the noninteractive case, which can be used, in particular, by  a single user trying to produce the same key from multiple readings of a physical source at different times.  The primitive accomplishing information reconciliation and privacy amplification noninteractively is known as a \emph{fuzzy extractor}; it is defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}

Fuzzy extractors consist of a pair of algorithms: \gen takes a source value $w$, and produces a key $r$ and a public helper value $p$.  The second algorithm \rep takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.  The security guarantee is that $r$ produces by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$, as long as $w$ comes from a high-quality distribution (traditionally, any distribution with sufficient min-entropy $m$). The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on strings over some alphabet $\mathcal{Z}$ of length $\ell$).

@@

More generally, let $B_t$ denote the number of points in a ball of radius $t$. For any $m$ and $t$, one can come up with a distribution of min-entropy $m$ such that the adversary can guess a correct $w'$ with probability $1/\lceil 2^m/B_t) \rceil\approx B_t 2^{-m}$: the distribution consists of all points in several nonoverlapping balls of radius $t$ (we need the space to be sufficiently large for the balls to fit). We thus call $m-\log B_t$ the \emph{minimum usable} entropy, denoted by $\Huse$. The previous paragraph shows that  no fuzzy extractor can handle all distributions of a given min-etropy $m$ if  $\Huse\le 0$.

@@

\paragraph{Our Contributions}
We provide the first constructions of computational fuzzy extractors that can be used for a large class of distributions with $\Huse\le 0$ over $\mathcal{Z}^\ell$ for a large alphabet $\mathcal{Z}$.  As explained above, such constructions cannot work without some restrictions on the distribution. 
It is secure when symbols in $w$ 
each have individual superlogarithmic min-entropy, even if they are arbitrarily correlated. Moreover,
a constant fraction of symbols in $w$ may have little entropy, as long as knowledge of their values does not reduce the entropy of the high-entropy symbols too much (see \defref{def:block guessable}).

We improve the entropy requirement in the second construction, which requires only a constant fraction of the symbols $w$ to have constant min-entropy conditioned on the previous symbols.
However, this improvement comes at a price to error-tolerance: whereas the first construction tolerates a constant fraction of errors, the second construction tolerates $\ell/\omega(\log\ell)$ errors.

\paragraph{Our Approach}
Our constructions are computationally secure. Indeed, known techniques for proving information-theoretically secure fuzzy extractors work for all distributions of a given entropy, and thus cannot be used to prove security for some distributions  with $\Huse\le 0$ (because then they would prove security for all distributions with $\Huse \le 0$, which we know is impossible.)

Most known constructions of fuzzy extractors put sufficient information in $p$ to recover $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
Fuller, Meng, and Reyzin~\cite{fuller2013computational}, in introducing computational fuzzy extractors, show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.  Instead, they suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent secret with computational entropy instead of recovering $w$.  We take the second approach.

Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}. We define and show two constructions of \emph{computational fuzzy conductors}. 
These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).

Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$. 
We need a strong version of point obfuscation, which is secure under composition.  
However, we note that for even this strong version, obfuscation of point programs is much simpler and more efficient than general obfuscation \lnote{omer, could you put in some references?}. In particular, it is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}. It can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1998perfectly}.

Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.  Let $w=w_1 \dots w_\ell$, for $w_i\in \mathcal{Z}$. In the first construction (\consref{cons:first construction}), for each $i$, $\gen$ flips a coin $c_i$ and either obfuscates $I_{w_i}$ or picks a random point $r_i$ and obfuscates $I_{r_i}$.  This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.  With a close value $w'$, $\rep$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.  For most locations $i$, \rep can determine whether $w_i$ or a random value was obfuscated.  Thus, most bits of $c_i$ are recoverable. To tolerate errors,  the set of coins $c_1\dots c_\ell$  is chosen at random from the codewords of an error correcting code. This construction conducts entropy from $w$ to $c$.

Note that obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates). We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it converts $w$ to a string of blocks and then applies the first construction. Each block is produced by  sampling several coordinates of $w$ and concatenating them. This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance. This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.  Note that, unlike in locally computable extractors, we can use the sampler multiple times and not worry about the fact that the same symbols is entering multiple blocks,  because correlations among blocks are not a problem for the first construction. Computational, rather than information-theoretic, analysis seems crucial for achieving this property.

\paragraph{Open Problems}
Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Alternatively, in case of burst errors~\cite{gilbert1960capacity}, multiple symbols from a small alphabet can be combined into a single symbol from a large alphabet}.  Although the sample-then-obfuscate construction remains secure with a small alphabet, because of its lower error tolerance, $\Huse \le 0$ only for large alphabets (for small alphabets, since $\Huse>0$,  there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}).
Constructing a computational fuzzy extractor with the above advantages and a small alphabet is an open problem.

Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within distance $t$ of $w$. The obfuscation is secure as long as $w$ comes from a distribution of sufficient minentropy; in particular, the entropy must be high enough so that $\Huse>0$. Our constructions do not provide obfuscators for proximity queries, because they leak more information than whether $x$ is within distance $t$ of $w$ (for example, they may provide some information about the actual distance or about which coordinates agree). Constructing an efficient obfuscator for proximity queries when $\Huse<0$ is an open problem.

\medskip
The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.

@@

\begin{definition}
\label{def:fuzzy min-ent}
A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
\[
\forall m\in \mathcal{M}, Pr_{w\in W}[\dis(w, m) \leq t] \leq 2^{-k}.
\]
\end{definition}
For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $m\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m)\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item On input $r, p$.
\item If $\rep(m, p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]\leq 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
\end{proof}
\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.  This means that fuzzy min-entropy is also a necessary condition for interactive solution.  %The original fuzzy extractors paper of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08} separated the starting entropy of $W$ and the desired error tolerance.  
If we wish to support parameter regimes where $\Huse\le 0$ there is some distribution with $\Hfuzz(W)=0$~(consider some fixed point $m\in\mathcal{M}$ and let $W$ be the uniform distribution over points within distance $t$).  Thus, if the analysis of a fuzzy extractor is for all input distributions with a particular $\Huse$, no key can be output when $\Huse\le 0$.   This motivates our restriction to meaningful classes of source distributions with $\Huse\le 0$.
%This means we inherently must talk about the security and errors together.
